---
title: "Lab2"
output: html_document
date: "2022-10-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
library(tidymodels)
library(corrplot)
library(ggthemes)
tidymodels_prefer()
```

```{r}
diamonds %>%
  head()
``` 
```{r}
diamonds %>% 
  select(is.numeric) %>% 
  cor() %>% 
  corrplot(type = 'lower', diag = TRUE, 
           method = 'square')
```
Which features are positively correlated with price? Do these make sense?
  Carat, x, y, and z, are all positively correlated with price. It makes sense that as there are more carats, the price of the diamond will also be higher. Since x, y, and z, are all dimensions of the diamond, it makes sense that as the diamond is bigger in any dimension, the price will also be higher.
  
Are any features negatively correlated with price?
  No, there don't seem to be any features that are negatively correlated with price. 
Which features are correlated with each other? Why do you think this might be?


```{r}
diamonds %>% 
  ggplot(aes(x = price, y = reorder(cut, price), fill = color)) + 
  geom_boxplot() +
  labs(y = "Cut", x = "Price") +
  theme_bw()
```

What do you learn from this plot about the relationship between price, cut, and color?
  It seems as though, the worse colors are priced higher across the cuts.There isn't a huge difference between the prices for the different cuts. 
  
```{r}
diamonds %>% 
  ggplot(aes(x = carat, y = reorder(color, carat))) + 
  geom_boxplot() +
  theme_bw() +
  labs(x = "Carat", y = "Color")
```

Explain why lower-quality colors tend to cost more.
  Color and carat seem to be negatively correlated. The "worse" colors tend to have higher carats. Since carat and price are highly positively correlated, this tends to follow that the worse colors are also negatively correlated with price. Hence, the lower-quality colors tend to cost more.
  
```{r}
diamonds %>% 
  ggplot(aes(x = price)) +
  geom_histogram(bins = 60) +
  theme_bw()
```

Create a single plot to visualize the relationship between cut, carat, and price.
```{r}

```

continuous vs continuous: correlation map
  single vs single: scatter plot
discrete vs continuous: box plot
discrete vs discrete: confusion matrix

# Data Splitting
```{r}
set.seed(3435)

diamonds_split <- initial_split(diamonds, prop = 0.80,
                                strata = price)
diamonds_train <- training(diamonds_split)
diamonds_test <- testing(diamonds_split)
```

How many observations are now in the training and testing sets, respectively? Report the exact number, not proportion.
  Training: 43152
  Test: 10788

What do you think the strata = price argument does? Take a guess, then use ?initial_split to verify.
  It breaks it up by price
  Verified: each sample is created within this variable. Binned into quartiles
  
  
# Linear Regression

Creating a Recipe
```{r}
simple_diamonds_recipe <-
  recipe(price ~ ., data = diamonds_train)
simple_diamonds_recipe
```
Note that . is a placeholder for “all other variables.”

```{r}
diamonds_recipe <- recipe(price ~ ., data = diamonds_train) %>% 
  step_dummy(all_nominal_predictors())
```

Name three step functions that weren’t used here and describe what they do
  step_zv creates a specification of a recipie step that will remove variables that contain only a single value
  step_other creates a specification of a recipe step that will potentially pool infrequently occurring values into an "other" category
  step_corr creates a specification of a recipe step that will potentially remove variables that have large absolute correlations with other variables
  
```{r}
lm_model <- linear_reg() %>% 
  set_engine("lm")
lm_wflow <- workflow() %>% 
  add_model(lm_model) %>% 
  add_recipe(diamonds_recipe)
lm_fit <- fit(lm_wflow, diamonds_train)
lm_fit %>% 
  # This returns the parsnip object:
  extract_fit_parsnip() %>% 
  # Now tidy the linear model object:
  tidy()
```
Explain what the intercept represents.

Describe the effect of carat. Is it a significant predictor of price? Holding everything else constant, what is the effect on price of a one-unit increase in carat?
  

predicted values for price for each observation in the training set:

```{r}
diamond_train_res <- predict(lm_fit, new_data = diamonds_train %>% select(-price))
diamond_train_res %>% 
  head()
```
attach a column with the actual observed price observations:
```{r}
diamond_train_res <- bind_cols(diamond_train_res, diamonds_train %>% select(price))
diamond_train_res %>% 
  head()
```
plot of predicted values vs. actual values:
```{r}
diamond_train_res %>% 
  ggplot(aes(x = .pred, y = price)) +
  geom_point(alpha = 0.2) +
  geom_abline(lty = 2) + 
  theme_bw() +
  coord_obs_pred()
```

linear model’s RMSE on the training data as a baseline
```{r}
rmse(diamond_train_res, truth = price, estimate = .pred)
```
We can create and view a “metric set” of RMSE, MSE, and R2 as shown:
```{r}
diamond_metrics <- metric_set(rmse, rsq, mae)
diamond_metrics(diamond_train_res, truth = price, 
                estimate = .pred)
```

```{r}
```





